Supplementary Material for 'New insights into the Weddell Sea ecosystem applying

### 2022-12-27 Manuscript/SupMaterial.Rmd
Review completed
Updated SM

---
title: Supplementary Material for 'New insights into the Weddell Sea ecosystem applying
  a network approach'
author: "Tomás I. Marina, Leonardo A. Saravia and Susanne Kortsch"
bibliography: ../WeddellSea.bib
output:
  word_document: default
  pdf_document: default
---

@@

load("QSS_summary_sep22.rda")
knitr::kable(all_data %>% dplyr::select(TrophicSpecies, QSS_all, QSS_ext, difQSS, Ad_pvalue) %>% arrange(., Ad_pvalue), digits = c(0,7,7,7,41), col.names = c("Species", "QSS_all", "QSS_ext", "difQSS", "AD_pvalue"), caption = "Summary of Quasi-Sign Stability (QSS) results before and after performing extinction simulations in the Weddell Sea food web. Ordered by increasing p-values of the Anderson-Darling test. QSS_all = Quasi-Sign Stability before the extinction (whole food web), QSS_ext = Quasi-Sign Stability after the extinction, difQSS = QSS difference between 'QSS_all' and 'QSS_ext', AD_pvalue = p-value for the Anderson-Darling test.")

>>>>

---
title: Supplementary Material for 'New insights into the Weddell Sea ecosystem applying
  a network approach'
author: "Tomás I. Marina, Leonardo A. Saravia and Susanne Kortsch"
bibliography: ../WeddellSea.bib
output:
  pdf_document: default
  word_document: default
---

@@

load("QSS_summary_sep22.rda")
knitr::kable(all_data %>% dplyr::select(TrophicSpecies, QSS_all, QSS_ext, difQSS, Ad_pvalue) %>% arrange(., Ad_pvalue), digits = c(0,7,7,7,41), col.names = c("Species", "QSS_all", "QSS_ext", "difQSS", "AD_pvalue"), caption = "Summary of Quasi-Sign Stability (QSS) results before and after performing extinction simulations in the Weddell Sea food web. Ordered by increasing p-values of the Anderson-Darling test. QSS_all = Mean Quasi-Sign Stability before the extinction (whole food web), QSS_ext = Mean Quasi-Sign Stability after the extinction, difQSS = QSS difference between 'QSS_all' and 'QSS_ext', AD_pvalue = p-value for the Anderson-Darling test.")
